Uncovering underlying high-level musical content in the temporal domain \\ \small Leveraging self-supervised deep neural networks, inductive bias, and aural skills to learn music embeddings with applications to MIR downstream tasks

### 2023-05-26 methods/subsections/implementation.tex
Updates from Overleaf

\subsection{Contrastive Learning of Musical Representations (CLMR)}

@@

The SampleCNN model \cite{Lee2018SampleCNN:Classification} takes 1D input data with a single channel. The first layer is a 1D convolutional layer with a kernel size of 3, a stride of 3, and 128 output channels. It is followed by batch normalization and ReLU activation.

@@

\begin{equation}
L_{\text{max}} = \max_{\text{item} \in \text{batch}}(\max(\text{length}(A_{\text{item}}), \text{length}(P_{\text{item}}), \text{length}(N_{\text{item}})))
\end{equation}

@@

>>>>

\section{Implementation details}
\subsection{Contrastive Learning of Musical Representations (CLMR)}

@@

The SampleCNN model \cite{Lee2018SampleCNN:Classification} takes 1D input data with a single channel and follows the next architecture:

\begin{tabular}{|p{4.5cm}|p{2cm}|p{2cm}|p{2cm}|p{2cm}|}
\hline
\textbf{Layer Type} & \textbf{In Channels} & \textbf{Out Channels} & \textbf{Kernel Size} & \textbf{Stride} \\
\hline
Conv1d + BatchNorm1d + ReLU & 1 & 128 & 3 & 3 \\
\hline
\multicolumn{5}{|c|}{The following layers are repeated depending on the strides and hidden parameters} \\
\hline
Conv1d + BatchNorm1d + ReLU + MaxPool1d & 128 & 128 & `<stride>` & `<stride>` \\
Conv1d + BatchNorm1d + ReLU + MaxPool1d & 128 & 128 & `<stride>` & `<stride>` \\
Conv1d + BatchNorm1d + ReLU + MaxPool1d & 128 & 256 & `<stride>` & `<stride>` \\
Conv1d + BatchNorm1d + ReLU + MaxPool1d & 256 & 256 & `<stride>` & `<stride>` \\
Conv1d + BatchNorm1d + ReLU + MaxPool1d & 256 & 256 & `<stride>` & `<stride>` \\
Conv1d + BatchNorm1d + ReLU + MaxPool1d & 256 & 256 & `<stride>` & `<stride>` \\
Conv1d + BatchNorm1d + ReLU + MaxPool1d & 256 & 256 & `<stride>` & `<stride>` \\
Conv1d + BatchNorm1d + ReLU + MaxPool1d & 256 & 256 & `<stride>` & `<stride>` \\
Conv1d + BatchNorm1d + ReLU + MaxPool1d & 256 & 512 & `<stride>` & `<stride>` \\
\hline
Conv1d + BatchNorm1d + ReLU & 512 & 512 & 3 & 1 \\
\hline
Dropout (optional) & - & - & - & - \\
\hline
Linear (Fully Connected) & 512 & 128 & - & - \\
\hline
\end{tabular}

@@

\subsubsection{Optimizer}

@@

\begin{equation}
L_{\text{max}} = \max_{\text{item} \in \text{batch}}(\max(\text{length}(A_{\text{item}}), \text{length}(P_{\text{item}}), \text{length}(N_{\text{item}})))
\end{equation}
\newpage
